Rigidity of Expectation: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-06-28 paper/Draft.tex
Finalized before2007 IR charts. Need to label them more clearly

\begin{eqnarray}
\begin{aligned}
\Sigma^y_{i,t|t} = \Sigma^y_{i,t|t-1} - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) H \Sigma^y_{i,t|t-1} 
\end{aligned}
\end{eqnarray}

@@

\begin{eqnarray}
\Delta \Sigma_{i,t+h|t} = \rho^{2h}\Delta  \Sigma_{i,t|t}  - \rho^{2h} \sigma^2_{\omega}
\end{eqnarray}

@@

This section first reproduces the results of a list of statistical tests of FIRE used in the existing literature in Table \ref{NullTestTable}, primarily following \citet{mankiw2003disagreement},  and then extends the tests replying upon data of individual uncertainty in Table \ref{RevEfficency} and \ref{WeakRevEfficiency}, in the spirit of forecasting efficiency by \citet{nordhaus1987forecasting}. It can be seen as an extension of what \citet{fuhrer2018intrinsic} does to mean forecast to uncertainty.

@@

Top panel in Table \ref{RevEffMeanTest} and bottom panel presents the results for mean forecast. Following \citet{fuhrer2018intrinsic}, I include median forecast available at time $t$ and $t-1$ as an indicator of past information for the revision regression. In the first column of each panel, I report the regression on a constant.

@@

The second to fourth column rejects the null of non-serial correlation for both CPI and PCE forecasts. The revision to CPI seems more efficient as serial correlation is with only one quarter lag. For PCE, the revisions in uncertainty are serially correlated with all past three quarters.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=6cm,height=4cm]{figures/CPIAU_ashocks_nmp.png}  
	\includegraphics[width=6cm,height=4cm]{figures/CPIAU_ashocks.png} \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFFE_ashocks_nmp.png} 
		\includegraphics[width=6cm]{figures/SPFFE_ashocks.png} \\
	\smallskip
	\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
		\includegraphics[width=6cm]{figures/SPFDisg_ab_ashocks.png} 
	\caption{Responses of Inflation and Professional Forecast Moments: 1984-2007}
	\label{ReplicateCoibionBefore2007}
\end{figure}

>>>>

\begin{eqnarray}\label{VarNIRv}
\begin{aligned}
\Sigma^y_{i,t|t} = \Sigma^y_{i,t|t-1} - \Sigma^y_{i,t|t-1} H'(H \Sigma^y_{i,t-1} H' +\Sigma^v) H \Sigma^y_{i,t|t-1} 
\end{aligned}
\end{eqnarray}

@@

\begin{eqnarray}\label{VarNIIndPop}
\Delta \Sigma_{i,t+h|t} = \rho^{2h}\Delta  \Sigma_{i,t|t}  - \rho^{2h} \sigma^2_{\omega}
\end{eqnarray}

@@

This section first reproduces a number of statistical tests of FIRE used seen existing literature in Table \ref{NullTestTable}, primarily following \citet{mankiw2003disagreement},  and then extends the tests relying on uncertainty in Table \ref{RevEfficency} and \ref{WeakRevEfficiency}, in the spirit of forecasting efficiency by \citet{nordhaus1987forecasting}. It is an extension of what \citet{fuhrer2018intrinsic} does to mean forecast to uncertainty.

@@

Top panel in Table \ref{RevEfficency} and bottom panel presents the results for mean forecast. Following \citet{fuhrer2018intrinsic}, I include median forecast available at time $t$ and $t-1$ as an indicator of past information for the revision regression. In the first column of each panel, I report the regression on a constant.

@@

The second to fourth column show positive serial correlation of revision in uncertainty for both CPI and PCE forecasts. The revision to CPI seems more efficient as serial correlation is with only one quarter lag. For PCE, the revisions in uncertainty are serially correlated with all past three quarters.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=7cm,totalheight=3cm]{figures/CPIAU_ashocks_nmp_before2007.png}  
	\includegraphics[width=7cm,totalheight=3cm]{figures/CPIAU_ashocks_before2007.png} \\
	\smallskip
	\includegraphics[width=7cm,totalheight=3cm]{figures/SPFFE_ashocks_nmp_before2007.png} 
		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFFE_ashocks_before2007.png} \\
	\smallskip
	\includegraphics[width=7cm,totalheight=3cm]{figures/SPFDisg_ab_ashocks_nmp_before2007.png} 
		\includegraphics[width=7cm,totalheight=3cm]{figures/SPFDisg_ab_ashocks_before2007.png} 
	\caption{Responses of Inflation and Professional Forecast Moments: 1984-2007}
	\label{ReplicateCoibionBefore2007}
\end{figure}
